### 2017-11-27 paper/sections/1_introduction.tex
paper: addresses #47
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But the policies for what data to evict and when to
evict are specific to the application's behavior and the system's configuration
(hardware, settings, etc.) so a new use case may prove to be a poor match for
the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using our data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can adapt to different workloads.

@@

Our target application, ParSplice~\cite{perez:jctc20150parsplice}, is
representative of applications that extensively use software-based caches.
ParSplice is a molecular dynamics simulation that uses a hierarchy of caches
and a single persistent key-value store to store both observed minima across a
molecule's equation of motion (EOM) and the hundreds or thousands of partial
trajectories calculated each second during a parallel job.  The fine-grained
data annotation capabilities provided by key-value storage is a natural match
for scientific simulations like ParSplice. But these simulations rely on a
mesh-based decomposition of a physical region and result in millions or
billions of mesh cells, where each cell contains materials, pressures,
temperatures and other characteristics that are required to accurately simulate
phenomena of interest.  Unfortunately, simulations of this size saturate the
capacity and bandwidth capabilities of a single node so we need more effective
data management techniques.

@@

The biggest challenge for ParSplice is properly sizing the caches in the
storage hierarchy.  The memory usage for a single cache that stores molecule
coordinates is shown in Figure~\ref{fig:cache-management}, where the thin solid
lines marked with \(\times\)'s are the existing configurations in ParSplice.
The default configuration uses an unlimited sized cache, shown by the ``No
Cache Management" line, but using this much memory for one cache is
unacceptable for HPC environments, where a common goal is to keep memory for
such data structures below 3\%\footnote{Anecdotally, we find this threshold
works well for HPC applications.  For reference, a 1GB cache for a distributed
file system is too large in LANL deployments.}. Furthermore, ParSplice deploys
a cache per 300 worker processes, so large simulations need more caches and
will use even more memory.  Users can configure ParSplice to evict data when
the cache reaches a threshold but this solution requires tuning and parameter
sweeps; the ``Cache (too small)" curve in Figure~\ref{fig:cache-management}
shows how a poorly configured cache can save memory but at the cost of
performance, which is shown by the text annotation to the right.  Even worse, this
threshold changes with different initial configurations and cluster setups so
tuning needs to be done for all system permutations.  Our dynamically sized
cache, shown by the thick line in Figure~\ref{fig:cache-management}, detects
key access patterns and re-sizes the cache accordingly.  Without tuning or
parameter sweeps, our solution saves more memory than a hand-tuned cache with a
negligible performance degradation (within the baseline's standard deviation)
and works for a variety of initial conditions.

% What is Mantle
To design more flexible cache management policies, like our solution in
Figure~\ref{fig:cache-management}, we use the data management language and
policy engine from the Mantle paper~\cite{sevilla:sc15-mantle}.  While Mantle
was designed for the narrow purpose of file system metadata load balancing,
this paper provides evidence that the approach is more broad.  Specifically,
the collection of abstractions in Mantle provide a general control plane that
improves the performance of metadata access. So in this paper we refer to
Mantle as a policy engine that injects policies written in our data management
language directly into a running service, such as a file system or key-value
store.  Rather than co-designing a policy directly into the service, which
requires domain-specific knowledge to find and change policies, we expose the
policies in a general way so even developers unfamiliar with the domain can
quickly deploy solutions.  We show that our framework:

>>>>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But the policies for what data to evict and when to
evict are specific to the application's behavior and the system's configuration
(hardware, settings, etc.) so a new workload may prove to be a poor match for
the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using our data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can be adapted to different workloads.

@@

Our example application, ParSplice~\cite{perez:jctc20150parsplice}, is
representative of an important class applications with similar working set
behaviors that extensively use software-based caches.  ParSplice is a molecular
dynamics simulation that uses a hierarchy of caches and a single persistent
key-value store to store both observed minima across a molecule's equation of
motion (EOM) and the hundreds or thousands of partial trajectories calculated
each second during a parallel job.  This workload is pervasive across
simulations that rely on a mesh-based decomposition of a physical region and
result in millions or billions of mesh cells, where each cell contains
materials, pressures, temperatures and other characteristics that are required
to accurately simulate phenomena of interest.  The fine-grained data annotation
capabilities provided by key-value storage is a natural match for these types
of scientific simulations.  Unfortunately, simulations of this size saturate
the capacity and bandwidth capabilities of a single node so we need more
effective data management techniques.

@@

The biggest challenge for ParSplice is properly sizing the caches in the
storage hierarchy.  The memory usage for a single cache that stores molecule
coordinates is shown in Figure~\ref{fig:cache-management}, where the thin solid
lines marked with \(\times\)'s are the existing configurations in ParSplice.
The default configuration uses an unlimited sized cache, shown by the ``No
Cache Management" line, but using this much memory for one cache is
unacceptable for HPC environments, where a common goal is to keep memory for
such data structures below 3\%\footnote{Anecdotally, we find this threshold
works well for HPC applications.  For reference, a 1GB cache for a distributed
file system is too large in LANL deployments.}. Furthermore, ParSplice deploys
a cache per 300 worker processes, so large simulations need more caches and
will use even more memory.  Users can configure ParSplice to evict data when
the cache reaches a threshold but this solution requires tuning and parameter
sweeps; the ``Cache (too small)" curve in Figure~\ref{fig:cache-management}
shows how a poorly configured cache can save memory but at the cost of
performance, which is shown by the text annotation to the right.  Even worse,
this threshold changes with different initial configurations and cluster setups
so tuning needs to be done for all system permutations.  Our dynamically sized
cache, shown by the thick line in Figure~\ref{fig:cache-management}, detects
key access patterns and re-sizes the cache accordingly.  Without tuning or
parameter sweeps, our solution saves more memory than a hand-tuned cache with a
negligible performance degradation (within the baseline's standard deviation),
works for a variety of initial conditions, and could generalize to similar
applications.

% What is Mantle
To design more flexible cache management policies, like our solution in
Figure~\ref{fig:cache-management}, we use the data management language and
policy engine from the Mantle paper~\cite{sevilla:sc15-mantle}.  While Mantle
was designed for the narrow purpose of file system metadata load balancing,
this paper provides evidence that the approach is more broad.  Specifically,
the collection of abstractions in Mantle provide a general control plane that
improves the performance of metadata access. So in this paper we refer to
Mantle as a policy engine that injects policies written in our data management
language directly into a running service, such as a file system or key-value
store.  Rather than co-designing a policy directly into the service, which
requires (1) domain-specific knowledge about the application to design an
effective policy and (2) service-specific knowledge to find and change
policies, we separate policies from mechanisms in a general way. By exposing
these policies (and not the mechanism) developers unfamiliar with the service
that their application uses can quickly deploy solutions based on their
domain-specific knowledge.  We show that our framework:
